---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# yesno

<!-- badges: start -->
[![lifecycle](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![R build status](https://github.com/poissonconsulting/yesno/workflows/R-CMD-check/badge.svg)](https://github.com/poissonconsulting/yesno/actions)
[![Codecov test coverage](https://codecov.io/gh/poissonconsulting/yesno/branch/master/graph/badge.svg)](https://codecov.io/gh/poissonconsulting/yesno?branch=master)
[![License: GPL2](https://img.shields.io/badge/License-GPL2-blue.svg)](https://www.gnu.org/licenses/old-licenses/gpl-2.0.en.html)
[![Tinyverse status](https://tinyverse.netlify.com/badge/yesno)](https://CRAN.R-project.org/package=yesno)
[![CRAN status](https://www.r-pkg.org/badges/version/yesno)](https://cran.r-project.org/package=yesno)
![CRAN downloads](https://cranlogs.r-pkg.org/badges/yesno)
<!-- badges: end -->

## Introduction

Provides two functions. 

The first, `yesno()`, asks a custom yes-no question with three variable responses.

The order and phrasing of the possible responses varies randomly to ensure the user consciously chooses (as opposed to automatically types their response).

The second, `yesno2()`, ask a yes-no question with two custom responses.

## Demonstration

```
yesno("Do you like ", R.Version()$nickname ,"?")
Do you like Bug in Your Hair?
1: Definitely
2: No way
3: No

Selection: 1
[1] TRUE

yesno("Do you like ", R.Version()$nickname ,"?")
Do you like Bug in Your Hair?
1: No way
2: Uhhhh... Maybe?
3: I agree

Selection: 2
[1] FALSE

> yesno2("Do you like this question?", yes = "I really do")
Do you like this question?
1: I really do
2: No

Selection: 1
[1] TRUE
```

## Installation

To install the latest release from [CRAN](https://cran.r-project.org)
```{r, eval=FALSE}
install.packages("yesno")
```

To install the developmental version from [GitHub](https://github.com/poissonconsulting/yesno)
```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("poissonconsulting/yesno")
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/yesno/issues).

[Pull requests](https://github.com/poissonconsulting/yesno/pulls) are always welcome.

## Code of Conduct

Please note that the yesno project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
